---
title: ''
author: ''
date: ''
output: 
  html_document:
    df_print: paged
    keep_md: true
  word_document:
    reference_docx: style.1.docx
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 6 * 1.67, fig.height = 6)


  load("data/data.RData")
  source("scripts/functions.R")

  library(tidyverse)
  library(descr)
  library(viridis)
  library(flextable)
  library(knitr)
  library(pander)
  library(sjPlot)
  library(rms)
  library(Hmisc)
  library(patchwork)
  library(survival)
  library(survminer)
# library(ggtern)

```


# Main Sample

The overall dataset includes `r nrow(data)` patients. Of these, only `r table(is.na(data$adm_primary_surgery_date_time))["TRUE"]` (`r round(table(is.na(data$adm_primary_surgery_date_time))["TRUE"] / nrow(data) * 100, 2)`%) are missing a surgery time, so these patients are removed from the dataset. 

```{r filter_surg}

  data_1_surg <- filter(data, !is.na(adm_primary_surgery_date_time)) # loses 892
  data_1_surg$out <- 1 # Flag for having surgery

```

There are different pathways that patients take, starting with their injury and leading up to their surgery. This could include multiple hospitals, ED visits, etc. However, the *main* pathway should be described by the following times:

- Time of Arrival to AE of treating Hospital (adm_ae_date_time)
- Time of Arrival to Ortho Ward (adm_orth_ward_date_time)
- Time of Surgery (adm_primary_surgery_date_time)
- Discharge date (dis_date)

Then there is a second, *alternative* pathway that is arrival -> orth -> surg -> discharge.   

At this point, to cover both of these pathways, we restrict the analysis to the patients with values for all 4 relevant time points. 

```{r filter_times}

  target_times <- c(
    "adm_ae_date_time",            
    "adm_orth_ward_date_time", 
    "adm_primary_surgery_date_time", 
    "dis_date"
  )

  cases <- complete.cases(data_1_surg[c("id", target_times)])
  tar <- data_1_surg[c("id", target_times)][cases, ]$id

  data_2_times <- filter(data_1_surg, id %in% tar) # 3553
  
```

Doing this takes the sample from `r nrow(data_1_surg)` to `r nrow(data_2_times)` patients (`r round(nrow(data_2_times) / nrow(data) * 100, 2)`% of the original dataset of `r nrow(data)` patients). 


```{r define_pathways}

# Create flags for the 2 pathways

  path_1 <- filter(
    data_2_times, 
    adm_ae_date_time < adm_orth_ward_date_time & 
    adm_orth_ward_date_time < adm_primary_surgery_date_time &
    adm_primary_surgery_date_time < dis_date
    )
# length(path_1$id) == length(unique(path_1$id))
  
  data_2_times$path_1 <- "No"
  data_2_times$path_1[data_2_times$id %in% path_1$id] <- "Yes"
# table(data_2_times$path_1)
  
  path_2 <- filter(
    data_2_times, 
    adm_ae_date_time < adm_primary_surgery_date_time & 
    adm_primary_surgery_date_time < adm_orth_ward_date_time &
    adm_orth_ward_date_time < dis_date
    )
# length(path_2$id) == length(unique(path_2$id))
  
  data_2_times$path_2 <- "No"
  data_2_times$path_2[data_2_times$id %in% path_2$id] <- "Yes"
# table(data_2_times$path_2)
  
  data_2_times <- data_2_times %>%
    mutate(
      pathway = case_when(
        path_1 == "Yes" ~ "Main Pathway", 
        path_2 == "Yes" ~ "Alternative Pathway"
      )
    )
  
  rm(path_1, path_2)
  
  data_3_paths <- filter(data_2_times, !is.na(pathway))

```

Then we delete those patients with complete times but that don't fall onto one of the two paths, taking the dataset from `r nrow(data_2_times)` to `r nrow(data_3_paths)` patients. Of these, `r table(data_3_paths$path_1)["Yes"]` patients are on the main path; and `r table(data_3_paths$path_2)["Yes"]` are on the alternative path. 

Just to confirm the dates are in the right order:

Main path (n = `r table(data_3_paths$path_1)["Yes"]`)
```{r}

  filter(data_3_paths, path_1 == "Yes") %>%
  select(id, target_times) %>%
    gather(event, date, -id) %>%
    arrange(id, date) %>%
    group_by(id) %>%
    mutate(order = row_number()) %>%
    filter(!is.na(date)) %>%
    ungroup() %>%
    group_by(event) %>%
    mutate(mean_order = mean(order)) %>%
    ungroup() %>%
    mutate(event = reorder(event, mean_order)) %>% 
  ggplot(aes(x = order, y = event, color = event)) +
    geom_jitter(size = 1, alpha = 0.2) +
    scale_color_viridis(guide = FALSE, discrete = TRUE) +
    theme_minimal() +
    theme(panel.grid = element_blank())

```

Alternative path (n = `r table(data_3_paths$path_2)["Yes"]`)
```{r}

  filter(data_3_paths, path_2 == "Yes") %>%
    select(id, target_times) %>%   
    gather(event, date, -id) %>%
    arrange(id, date) %>%
    group_by(id) %>%
    mutate(order = row_number()) %>%
    filter(!is.na(date)) %>%
    ungroup() %>%
    group_by(event) %>%
    mutate(mean_order = mean(order)) %>%
    ungroup() %>%
    mutate(event = reorder(event, mean_order)) %>%
  ggplot(aes(x = order, y = event, color = event)) +
    geom_jitter(size = 1, alpha = 0.2) +
    scale_color_viridis(guide = FALSE, discrete = TRUE) +
    theme_minimal() +
    theme(panel.grid = element_blank())

```


```{r time_outcomes}

# Create the all time variables
  data_3_paths <- mutate(
    data_3_paths, 
    ae_orth_diff = difftime( # Path 1 and 2
        adm_orth_ward_date_time, adm_ae_date_time, units = "hours"
        ) %>% as.numeric(),
    orth_surg_diff = difftime( # Path 1 (negative for path 2)
        adm_primary_surgery_date_time, adm_orth_ward_date_time, units = "hours"
        ) %>% as.numeric(),
    ae_surg_diff = difftime( # Path 1 and 2
        adm_primary_surgery_date_time, adm_ae_date_time, units = "hours"
        ) %>% as.numeric(),
    surg_orth_diff = difftime( # Path 2 (negative for path 1)
        adm_orth_ward_date_time, adm_primary_surgery_date_time, units = "hours"
        ) %>% as.numeric(),
    ae_orth_diff = difftime( # Path 1 and 2
        adm_orth_ward_date_time, adm_ae_date_time, units = "hours"
        ) %>% as.numeric()
    )
        
```

Finally, we want to remove patients with an AE to surgery time > 120 hours. 
```{r filter_surg_times}

  data_3_5d <- filter(data_3_paths, ae_surg_diff <= 120) %>%
    mutate(surg48 = factor(ifelse(ae_surg_diff > 48, "Yes", "No")), 
           age_z = scale(age, scale = FALSE)) 

```

Doing this takes the sample from `r nrow(data_3_paths)` to `r nrow(data_3_5d)` patients (`r round(nrow(data_3_5d) / nrow(data) * 100, 2)`% of the original dataset of `r nrow(data)` patients). 

```{r}
  data_4_pmain_5d <- filter(data_3_5d, path_1 == "Yes") 

  data_4_palt_5d <- filter(data_3_5d, path_2 == "Yes") 

```




# Main pathway analysis (n = `r nrow(data_4_pmain_5d)`)

## Outcomes 

```{r}

  labs <- c("AE to Orth Ward", "Orth Ward to Surgery", "AE to Surgery")
  
  levs <- c("ae_orth_diff", "orth_surg_diff", "ae_surg_diff")

  data_4_pmain_5d_long <- data_4_pmain_5d %>%
    select(ae_orth_diff, orth_surg_diff, ae_surg_diff) %>%
    gather(type, value) %>%
    mutate(type = factor(type, levels = levs, labels = labs)) 

```

```{r}
  
  ggplot(data_4_pmain_5d_long, aes(y = value, x = type)) +
    geom_jitter(height = 0, width = 0.2, alpha = 0.2) +
    geom_boxplot(alpha = 0.2, color = "white", size = 1, outlier.alpha = 0) +
    facet_wrap(~type, nrow = 1, scales = "free_x") +
    ylab("Hours") +
    theme(axis.text.x = element_blank(), 
          panel.grid = element_blank(), 
          panel.background = element_rect(fill = "grey")) +
    xlab("")
```

## Table 1

```{r}

  descript <- data_4_pmain_5d %>%
    select(
      sex, age, marr_status, 
      los, has_med_card, adm_asa_grade, 
      ae_orth_diff, orth_surg_diff, ae_surg_diff, 
      mdro, anticoag)

  data_frame(
    Variable = name.1(descript),
    Missing   = n.miss(descript),
    "Mean SD or n (%)" = summary.1(descript),
    "Median [IQR]" = med.iqr(descript),
    "(Min, Max)" = min.max(descript)
    ) %>% 
  flextable() 
  
```


## Time to event models

### KM Plots (crude)

```{r}

  surplot <- function(sf, titl, brk = 24, lm = 120, show48 = TRUE, 
                      gd = TRUE){
    
    hour48 <- summary(sf, times = 48)

    p1 <- ggsurvplot(
      sf, 
      conf.int = FALSE, 
      surv.median.line = "hv", 
      risk.table = FALSE, 
      break.x.by = brk, 
      xlab = "Hours", 
      xlim = c(0, lm)
      ) 
  
    if(gd == TRUE){
      p2 <- p1$plot + 
        ggtitle(titl) + 
        scale_color_discrete() +
        theme(plot.title = element_text(size = 12))
    } else {
      p2 <- p1$plot + 
        ggtitle(titl) + 
        scale_color_discrete(guide = FALSE) +
        theme(plot.title = element_text(size = 12))
    }
    
    if(show48 == TRUE){
    p2 <- p2 +  
      geom_segment(x = hour48$time, xend = hour48$time, 
                   y = 0, yend = hour48$surv) +
      geom_segment(x = 0, xend = hour48$time, 
                   y = hour48$surv, yend = hour48$surv)
    }
    
    return(p2)
      
  }

```


```{r}

  sf_ae_orth_mdro <- survfit(Surv(ae_orth_diff, out) ~ mdro, 
                            data = data_4_pmain_5d)
  sf_orth_surg_mdro <- survfit(Surv(orth_surg_diff, out) ~ mdro, 
                              data = data_4_pmain_5d)
  sf_ae_surg_mdro <- survfit(Surv(ae_surg_diff, out) ~ mdro, 
                            data = data_4_pmain_5d)
  
  surplot(sf_ae_orth_mdro, "AE to Orthopaedic Ward", 
          show48 = FALSE) | 
  surplot(sf_orth_surg_mdro, "Orthopaedic Ward to Surgery", 
          show48 = FALSE, gd = FALSE) | 
  surplot(sf_ae_surg_mdro, "AE to Surgery", 
          show48 = FALSE, gd = FALSE)

```

Proportion AE to surgery >= 48 hours (compare survival proportions)

```{r}

  summary(sf_ae_surg_mdro, times = 48)

```

### Cox models (crude and adjusted)

All the tables report HRs, so that values < 1 indicate *longer* times to surgery. 

Times from AE (the total times)

```{r}

  s_ae_orth_acoag   <- with(data_4_pmain_5d, Surv(ae_orth_diff, out))
  s_orth_surg_acoag <- with(data_4_pmain_5d, Surv(orth_surg_diff, out))
  s_ae_surg_acoag   <- with(data_4_pmain_5d, Surv(ae_surg_diff, out))

  ddist <- datadist(data_4_pmain_5d) # For RMS
  options(datadist = "ddist")

  cox1 <- coxph(s_ae_orth_acoag ~ mdro, data = data_4_pmain_5d)
  cox2 <- coxph(s_ae_orth_acoag ~ mdro + anticoag + rcs(age_z, 5) + 
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
                data = data_4_pmain_5d)
  
  cox3 <- coxph(s_orth_surg_acoag ~ mdro, data = data_4_pmain_5d)
  cox4 <- coxph(s_orth_surg_acoag ~ mdro + anticoag + rcs(age_z, 5) + 
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
                data = data_4_pmain_5d)
  
  cox5 <- coxph(s_ae_surg_acoag ~ mdro, data = data_4_pmain_5d)
  cox6 <- coxph(s_ae_surg_acoag ~ mdro + anticoag + rcs(age_z, 5) + 
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
                data = data_4_pmain_5d)

  tab_model(
    cox1, cox2, cox3, cox4, cox5, cox6,
    dv.labels = c(
      rep("AE to Orthopeadic Ward", 2), 
      rep("Orthopeadic Ward to Surgry", 2), 
      rep("AE to Surgery", 2)
    )
  )

```



# Alternative pathway analysis (n = `r nrow(data_4_palt_5d)`)

## Outcomes 

```{r}

  labs <- c("AE to Surgery", "Surgery to Orth Ward", "AE to Orth Ward")

  levs <- c("ae_surg_diff", "surg_orth_diff", "ae_orth_diff")

  data_4_palt_5d_long <- data_4_palt_5d %>%
    select(ae_surg_diff, surg_orth_diff, ae_orth_diff) %>%
    gather(type, value) %>%
    mutate(type = factor(type, levels = levs, labels = labs))
  
```


```{r}
  
  ggplot(data_4_palt_5d_long, aes(y = value, x = type)) +
    geom_jitter(height = 0, width = 0.2, alpha = 0.2) +
    geom_boxplot(alpha = 0.2, width = 0.4, color = "white", 
                 size = 1, outlier.alpha = 0) +
    facet_wrap(~type, nrow = 1, scales = "free_x") +
    ylab("Hours") +
    theme(axis.text.x = element_blank(), 
          panel.grid = element_blank(), 
          panel.background = element_rect(fill = "grey")) +
    xlab("") +
    coord_cartesian(ylim = c(0, 240))
```

## Table 1

```{r}

  descript <- data_4_palt_5d %>%
    select(
      sex, age, marr_status, 
      los, has_med_card, adm_asa_grade, 
      ae_orth_diff, surg_orth_diff, ae_surg_diff, 
      mdro, anticoag)

  data_frame(
    Variable = name.1(descript),
    Missing   = n.miss(descript),
    "Mean SD or n (%)" = summary.1(descript),
    "Median [IQR]" = med.iqr(descript),
    "(Min, Max)" = min.max(descript)
    ) %>% 
  flextable() 
  
```


## Time to event models

### KM Plots (crude)

```{r}

  
  sf_ae_surg_mdro <- survfit(Surv(ae_surg_diff, out) ~ mdro, 
                            data = data_4_palt_5d)
  sf_surg_orth_mdro <- survfit(Surv(surg_orth_diff, out) ~ mdro, 
                              data = data_4_palt_5d)
  sf_ae_orth_mdro <- survfit(Surv(ae_orth_diff, out) ~ mdro, 
                            data = data_4_palt_5d)

  
  surplot(sf_ae_surg_mdro, "AE to Surgery", show48 = FALSE) | 
  surplot(sf_surg_orth_mdro, "Surgery to Orthopaedic Ward", show48 = FALSE, 
          gd = FALSE) | 
  surplot(sf_ae_orth_mdro, "AE to Orthopaedic Ward", show48 = FALSE, 
          gd = FALSE)

```

Proportion >= 48 hours (compare survival proportions)

```{r}

  summary(sf_ae_surg_mdro, times = 48)

```


### Cox models (crude and adjusted)

All the tables report HRs, so that values < 1 indicate *longer* times to surgery. 

```{r}

  s_ae_surg_acoag   <- with(data_4_palt_5d, Surv(ae_surg_diff, out))
  s_surg_orth_acoag <- with(data_4_palt_5d, Surv(surg_orth_diff, out))
  s_ae_orth_acoag   <- with(data_4_palt_5d, Surv(ae_orth_diff, out))

  ddist <- datadist(data_4_palt_5d) # For RMS
  options(datadist = "ddist")

  cox1 <- coxph(s_ae_surg_acoag ~ mdro, data = data_4_palt_5d)
  cox2 <- coxph(s_ae_surg_acoag ~ mdro + anticoag + rcs(age_z, 5) + 
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
                data = data_4_palt_5d)
  
  cox3 <- coxph(s_surg_orth_acoag ~ mdro, data = data_4_palt_5d)
  cox4 <- coxph(s_surg_orth_acoag ~ mdro + anticoag + rcs(age_z, 5) + 
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
                data = data_4_palt_5d)
  
  cox5 <- coxph(s_ae_orth_acoag ~ mdro, data = data_4_palt_5d)
  cox6 <- coxph(s_ae_orth_acoag ~ mdro + anticoag + rcs(age_z, 5) + 
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
                data = data_4_palt_5d)


  tab_model(
    cox1, cox2, cox3, cox4, cox5, cox6,
    dv.labels = c(
      rep("AE to Surgery", 2), 
      rep("Surgry to Orthopeadic Ward", 2), 
      rep("AE to Orthopeadic Ward", 2)
    )
  )


```

The notable result in the table above is that there is MDRO status is associated with substantial increases in the time between surgery and the orthopeadic ward, but that this association is explained away by adjustment for potential confounders, including hospital. 

Here is the KM plot for that unadjusted effect in the `r nrow(data_4_palt_5d)` patients on the alternative pathway. 

```{r}

  sf_ae_orth_mdro <- survfit(Surv(ae_orth_diff, out) ~ mdro, 
                            data = data_4_palt_5d)
  

  surplot(sf_ae_orth_mdro, "AE to Orthopaedic Ward", show48 = FALSE)
   
```

However, this is really explained by hospital. 

First, here is the KM plot for hospital for patients on the alterntive pathway. 

```{r}

  df <- group_by(data_4_palt_5d, hosp) %>%
      summarise(mean_ae_orth = median(ae_orth_diff, na.rm = TRUE)) %>%
      right_join(data_4_palt_5d, by = "hosp") %>%
      mutate(hosp = reorder(factor(hosp), mean_ae_orth))

  sf_ae_orth_mdro <- survfit(Surv(ae_orth_diff, out) ~ hosp, 
                            data = df)

  surplot(sf_ae_orth_mdro, "AE to Orthopaedic Ward", lm = 240, show48 = FALSE)
  
```

You can see that the Mater and Drogheda are outliers with longer times to ward, and Tullamore and Connolly have relatively shorter times. 

Now, if we look at the MDRO status of patients on the alt path in each hospital, ordered by their median times to ward (as they are ordered in the KM plot above), we see that a disproportionate number of MDRO cases happen to be in the hospitals with longer times. 

```{r}

  g1 <- ggplot(df, aes(x = hosp, fill = mdro)) +
    geom_bar() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_fill_discrete(guide = FALSE) + 
    ggtitle("1694 patients on alternative path")

  g2 <- ggplot(df, aes(x = hosp, fill = mdro)) +
    geom_bar(position = "fill") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      scale_fill_discrete() +
      ylab("Proportion") +
      geom_hline(yintercept = 0.044, color = "white", linetype = "dashed", 
                 size = 1.5) +
      coord_cartesian(ylim = c(0, 0.5))
  
  g1 + g2 
  
```

So the main issue here is that Mater and Drogheda, which both have > average % of MDRO also have longer delays in getting to the ward. Meanwhile Connolly has no mdro on the alt path and Midland has the average %, but they have relatively shorter time to ward. 

Here is the same info, but now with patient level times to ward plotted. 

```{r}

  ggplot(df, aes(y = ae_orth_diff, color = mdro, 
                             x = interaction(mdro, hosp))) + 
    geom_jitter(width = 0.2) +
    geom_boxplot(alpha = 0.1, color = "black", fill = "white") +
    facet_wrap(~hosp, scales = "free_x", nrow = 1) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
          strip.text = element_blank()) +
    xlab("MDRO status:Hospital") +
    ylab("AE to Ward Time (hours)") +
    ggtitle("AE to Ward in Alt path patients") 

```

This is the same plot, but with times log10 transformed so we can see them better.

```{r}

  ggplot(df, aes(y = ae_orth_diff, color = mdro, 
                             x = interaction(mdro, hosp))) + 
    scale_y_continuous(trans = "log10") +
    geom_jitter(width = 0.2) +
    geom_boxplot(alpha = 0.1, color = "black", fill = "white") +
    facet_wrap(~hosp, scales = "free_x", nrow = 1) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
          strip.text = element_blank(), 
          panel.grid = element_blank()) +
    xlab("MDRO status:Hospital") +
    ylab("AE to Ward Time (log10(hours))") +
    ggtitle("AE to Ward in Alt path patients") +
    annotation_logticks(sides = "l") 

```

Just for comparison, you can see that the times to surgery (all capped at < 5 days) aren't as variable, and so the impact of adjusting the Cox models for hospital isn't a prominent when AE to Surgery is the outcome. 

```{r}
    ggplot(df, aes(y = ae_surg_diff, color = mdro, 
                             x = interaction(mdro, hosp))) + 
    scale_y_continuous(trans = "log10") +
    geom_jitter(width = 0.2) +
    geom_boxplot(alpha = 0.1, color = "black", fill = "white") +
    facet_wrap(~hosp, scales = "free_x", nrow = 1) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
          strip.text = element_blank(), 
          panel.grid = element_blank()) +
    xlab("MDRO status:Hospital") +
    ylab("AE to Ward Time (log10(hours))") +
    ggtitle("AE to Ward in Alt path patients") +
    annotation_logticks(sides = "l") 
```

Same idea, reflected in the KM plot (less variability in time to surgery by hospital)

```{r}


  sf_ae_surg_mdro <- survfit(Surv(ae_surg_diff, out) ~ hosp, 
                            data = df)
  
  surplot(sf_ae_surg_mdro, "AE to Surgery", show48 = FALSE)
```

And a much smaller effect to start with (unadjusted KN plot for time to surgery by MDRO status in patients on the alternative path)

```{r}

  sf_ae_orth_mdro <- survfit(Surv(ae_surg_diff, out) ~ mdro, 
                            data = df)

   surplot(sf_ae_orth_mdro, "AE to Surgery", show48 = FALSE)
   
```



# Supplemental


MDRO status by pathway
```{r}

  g1 <- data_3_paths %>%
    select(id, mdro, pathway) %>%
  ggplot(aes(x = pathway, fill = mdro)) +
    geom_bar(position = "fill") + 
    scale_fill_viridis(guide = FALSE, discrete = TRUE, end = 0.8) +
    xlab("") +
    ylab("Proportion of MDRO cases")

  g2 <- data_3_paths %>%
    select(id, mdro, pathway) %>%
  ggplot(aes(x = pathway, fill = mdro)) +
    geom_bar() + 
    scale_fill_viridis(discrete = TRUE, end = 0.8) +
    xlab("") +
    ylab("Number of MDRO cases")
  
  g1 | g2
  
  rm(g1, g2)

```

```{r}
 
   tbl <- with(data_3_paths, table(mdro, pathway))
   cont_table_2(tbl) %>% pander()
  
```


Relative number of patients on each pathway (n = `r nrow(data_3_5d)` patients with no missing time values and AE to surgery < 5 days)
```{r}

  df <- group_by(data_3_5d, hosp) %>%
    summarise(hosp_n = n()) %>%
    right_join(data_3_5d, by = "hosp") %>%
    mutate(hosp = reorder(factor(hosp), hosp_n))

  g1 <- ggplot(df, aes(x = hosp, fill = pathway)) +
    geom_bar() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_fill_discrete(guide = FALSE)

  g2 <- ggplot(df, aes(x = hosp, fill = pathway)) +
    geom_bar(position = "fill") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
      scale_fill_discrete("") +
      ylab("Proportion")

  g1 + g2
  
```


Logistic model for odds of surg > 48 hours for patients on the main pathyway

```{r}

  lgt1 <- glm(surg48 ~ mdro, 
              data = data_4_pmain_5d, 
              family = binomial(logit))
  
  lgt2 <- glm(surg48 ~ mdro + anticoag + rcs(age_z, 5) +
                  sex + adm_asa_grade + has_med_card +
                  hosp, 
              data = data_4_pmain_5d, 
              family = binomial(logit))
  
  tab_model(lgt1, lgt2, dv.labels = rep("AE to Surgery > 48 hours", 2))


```


```{r}

  tar <- data_3_5d$id

  data$sample <- "Out"
  data$sample[data$id %in% tar] <- "In"
  

```


In (both pathways) vs Out of sample characteristics

```{r}

  suppl.table <- data %>%
    select(
      arm = sample, sex, age, marr_status, los, has_med_card, 
      adm_asa_grade, mdro, anticoag
      )

  out_sample <- filter(suppl.table, arm == "Out") %>% select(-arm)
  in_sample <- filter(suppl.table, arm == "In") %>% select(-arm)

  
  data_frame("Variable" = name.1(select(suppl.table, -arm)),
             "Observations" = as.numeric(n.miss(select(suppl.table, -arm))),
             "Total"    = summary.2(select(suppl.table, -arm)),
             "Out (n = 5115)" = summary.2(out_sample),
             "In (n = 13003)" = summary.2(in_sample),
             "Test p-value" = tests.2(suppl.table)) %>% 
    knitr::kable()

  
```


```{r publication_qualityplots}

#  ggsave("XXX", device = "pdf", dpi = 600)

```

```{r if_html, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

# use flextable (works for MD files on github too)

```

```{r if_word, eval = !knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

# use kable

```

```{r code_book}

#  print(summarytools::dfSummary(data), method = "render")

```

```{r sysinfo}

  DescTools::SysInfo()

```



